### 2014-10-01 paper/include/background.tex
written on bg

As m

\begin{figure}[t]
    \centering
    \subfigure[DRAM throughput loss]{
        \centering
        \includegraphics[width=0.33\textwidth]{dram_throughput}
        \label{fig:dram_throughput}
    }
    \subfigure[DRAM power consumption]{
        \centering
        \includegraphics[width=0.33\textwidth]{dram_power}
        \label{fig:dram_power}
    }%
    \caption{Projections on DRAM throughput loss and power consumption \cite{raidr}.}
    \label{fig:dram_data_proj}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[DRAM throughput loss]{
        \centering
        \includegraphics[width=0.33\textwidth]{dram_throughput}
        \label{fig:dram_throughput}
    }
    \subfigure[DRAM power consumption]{
        \centering
        \includegraphics[width=0.33\textwidth]{dram_power}
        \label{fig:dram_power}
    }
    \caption{Projections on DRAM throughput loss and power consumption \cite{raidr}.}
    \label{fig:dram_data_proj}
\end{figure}

The trends of DRAM chips is that they become larger and larger. In practice, this is realized to a high degree by adding additional rows in the banks. The rows could instead - or also - been made longer by adding DRAM cells, but this solution is not favourable as it increases the power consumption per row access.
